---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(classdata)
head(ames)

View(ames)
range(ames$Sale_Price, na.rm = TRUE)


```

# Lab report #2

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(classdata)
head(ames)
View(ames)
str(ames$`Sale Price`)
range(ames$`Sale Price`, na.rm = TRUE)
```

1. 

Cameron:
Parcel ID
Address
Style 
Occupancy 

Neel:
Sale Date - When the rprooperty was sold
Sale Price - How much the property sold for
Multi Sale - Was the Sale part of a package
YearBuilt - When the house was constructed

David:
Acres - Acres of the lot.
TotalLivingArea (sf) - Total living area in square feet. 
Bedrooms - Number of bedrooms.
FinishedBsmtArea (sf) - Total area of the finished basement in square feet.

Ben:
LotArea (sf)
AC
FirePlace
Neighborhood

2. Sale_Price

3. The main variable is Sale price. The range goes from 0 - 2,050,0000.



4. 

Cameron-TotalLivingArea

