---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


# Lab report #2

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(classdata)
head(ames)
View(ames)

range(ames$Sale_Price, na.rm = TRUE)

filtered_ames <- ames[ames$`Sale Price` <= 1000000, ]
hist(filtered_ames$`Sale Price`,
     main = "Histogram of Filtered Sale Price",
     xlab = "Sale Price",
     col = "blue",
     border = "black")

```



```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(classdata)
head(ames)
View(ames)
str(ames$`Sale Price`)
range(ames$`Sale Price`, na.rm = TRUE)
range(ames$`LotArea(sf)`, na.rm = TRUE)
```

1. 
Cameron:
Parcel ID
Address
Style 
Occupancy 

Neel:
Sale Date - When the rprooperty was sold.
Sale Price - How much the property sold for
Multi Sale - Was the Sale part of a package
YearBuilt - When the house was constructed

David:
Acres - Acres of the lot.
TotalLivingArea (sf) - Total living area in square feet. 
Bedrooms - Number of bedrooms.
FinishedBsmtArea (sf) - Total area of the finished basement in square feet.

Ben:
LotArea (sf) - lot area is a numerical attribute. It describes the tota; square area of the lot in square feet. The range is from 0 to 523,228.
AC - AC is a lagocial attribute. It answers the question of if the property has AC. The answer is yes or no.
FirePlace - FirePLace is also a logical attribute. It shares the same answer options as AC.
Neighborhood - Neighborhood is a factor variable. This has levels of the neighborhood area in Ames.

2. Sale_Price

3. The main variable is Sale price. The range goes from 0 - 2,050,0000.
The graph from the sale and frequency shows from left to right, it has a higher frequency and than it drops and lowers into a right scheme.



4. 
Cameron-TotalLivingArea


Neel - Arces
```{r Attribute_Acres include=FALSE}
library(classdata)
plot(ames$Acres, ames$`Sale Price`,main = "Scatterplot of Sale Price vs. Acres",
  xlab = "Acres", ylab = "Sale Price", col = "blue", pch = 16)
```
Acres Explanation
The range of the Acres goes from 0.001 - 12.012 acres(after removing the house(s) with 0 values).
Most of the data points are clustered around Acres values less than 2, indicating that the majority of properties are on small lots, the sale price for these properties have high density of points between 0 - 500,000.
There are a few outliers with high Acres and high prices.

Ben attribute - LotArea(sf)
```{r Attribute_LotArea, include=FALSE}
library(ggplot2)
library(classdata)
p <- ggplot(ames, aes(x = `LotArea(sf)`, y = `Sale Price`)) +
  geom_point() +
  labs(x = "Lot Area (sf)", y = "Sale Price", title = "Scatterplot of Lot Area vs. Sale Price") +
  theme_minimal()

print(p)
```
Ben - LotArea explanation
This graph has some major issues with it. For starters, it has some huge outliers. There is a big outlier past 5e+05 on the x axis, and multiple more that are way up at the top left of the graph. There isn't a ton that can be taken away from this graph. The outliers prevent any major takeaways and even then, it doesn't look like there are any major correlations with the data that is in the bottom left.


David - Bedrooms
library(classdata)

# Scatterplot of Sale Price vs. Bedrooms
plot(ames$Bedrooms, ames$`Sale Price`, 
     main = "Scatterplot of Sale Price vs. Bedrooms",
     xlab = "Number of Bedrooms", 
     ylab = "Sale Price", 
     col = "blue", 
     pch = 16)
     
Explanation: 
From the data and plot, I observed that sale prices generally increase with the number of bedrooms, but the trend is inconsistent. There is considerable variability, particularly for houses with more than 4 bedrooms, with some larger houses showing unexpectedly low prices. This indicates that factors beyond just the number of bedrooms, like location or property condition, have a significant influence on sale price.


  


