---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(classdata)
head(ames)

View(ames)
range(ames$Sale_Price, na.rm = TRUE)

library(classdata)
head(ames)
View(ames)

```

# Lab report #2

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.
<<<<<<< HEAD
=======

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(classdata)
head(ames)
View(ames)
```

1. 

Cameron:
Parcel ID
Address
Style 
Occupancy 

Neel:
Sale Date 
Sale Price
Multi Sale
YearBuilt

David:
Acres
TotalLivingArea (sf)
Bedrooms
FinishedBsmtArea (sf)

Ben:
LotArea (sf)
AC
FirePlace
Neighborhood

2. Sale_Price

3. The main variable is Sale price. The range can be found by running



4. 

Cameron-TotalLivingArea

